\documentclass[10pt]{Article}
\topmargin=-0.5in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=-0.25in %length of margin on sides for odd pages
\evensidemargin=-0.25in %length of margin on sides for even pages
\textwidth=7.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase this attribute to increase white space in between headers and the top of the page
\textheight=11in %How tall the text body is allowed to be on each page
\pagenumbering{gobble}
\usepackage{enumitem}
\usepackage[none]{hyphenat}
\usepackage[margin=0.3in]{geometry}
\usepackage[compact]{titlesec}
%\titleformat{command}[shape]{format}{label}{sep}{before-code}[after-code]
\titleformat*{\section}{\normalsize\bfseries}


\begin{document}
\begin{center}
\centering {\Large \bf Austin Levesque}\\
\vspace{.5ex}
56 Old Oregon Rd, Cortlandt Manor, NY 10567
\end{center}
\noindent{\bf Phone:} (845)-667-2975\hfill{\bf LinkedIn:} https://www.linkedin.com/in/austinlvsq/\\
\noindent{\bf Email:} Austin.lvsq@gmail.com\\
\line(1,0){570}

\section*{Career Objective}
\begin{itemize}[topsep=1ex, itemsep=.5ex, parsep=0ex, partopsep=.75ex]
	\item[]To obtain a full time position where I am able to leverage the skills I acquired through software engineering and information technology to aid a team in delivering the highest quality service possible.
\end{itemize}

\section*{Education}
\begin{itemize}[topsep=1ex, itemsep=.5ex, parsep=0ex, partopsep=.75ex]
	\item[]{{\bf Rochester Institute of Technology \hfill Rochester, New York}}
  \item[] Bachelors of Science in Information Technology. \hfill Graduated May 2017.
  \item[] Minor: Economics.
\end{itemize}

\section*{Skills}
\begin{itemize}[topsep=1ex, itemsep=.5ex, parsep=0ex, partopsep=.75ex]
	\item[]{\bf Languages:} Java, Javascript, PHP, Swift, SQL, C++, Python, Powershell.
	\item[]{\bf IT:} Windows Systems Administration, DNS, DHCP, Microsoft System Center Configuration Manager.
\end{itemize}

\section*{Projects}
\begin{itemize}[topsep=1ex, itemsep=.5ex, parsep=0ex, partopsep=.75ex]
	\item[]{\bf Senior Design \& Development Project} (Senior Project, Fall 2016 \& Spring 2017)\\
	Worked as part of an international team to design, develop, and implement a Course Assesment tool in PHP, and java utilizing the Java Spring Framework and Docker Containers.
	\item[]{\bf NodeJs Vending Machine:} (Computer Science House Major Project, Fall 2016 \& Spring 2017) Continuing Project\\
	Inherited the remains of a project written in Javascript using the NodeJS framework, and refactored parts of the codebase to enable others to readily continue working on the project.
	\item[]{\bf Client \& Server Connect Four Implementation} (Concepts of Parallel and Distributed Systems, Fall 2014)\\
  Developed both the server side and client side of a networked Connect Four game using UDP and TCP in Java over a fifteen week period.
	\item[]{\bf Monte Catrlo Simulation of Networks:}(Data Communications, Spring 2014)\\
	Generated models using Monte Carlo simulation to test the energy requirements and network connectivity of small world, scale free, and ad hoc networks over the course of a semester.
	\item[]{\bf Networked vending machines} (Software Engineering, Spring 2013)\\
	Engineered a suite of applications to manage vending machines in Java with a team of four students with two product releases in a ten week period using agile methodologies.
\end{itemize}

\section*{Work Experience}
\begin{itemize}[topsep=1ex, itemsep=.5ex, parsep=0ex, partopsep=.75ex]
	\item[]{{\bf Lower Hudson Regional Information Center} \hfill {\bf May 2017 to Current.}}\\
	BOCES, Managed Information Technology Department \hfill http://www.lhric.org/\\
	Currently working as part of a team of information technology professionals to offer Level 1, and Level 2 Support to 30+ School Districts in Westchester County, Ny.
	I have participated in projects working with Windows Update Servers, Backup Management, DNS and DHCP configuration, Managing print services, and Creating \& Deploying Desktop Images.
	\item[]{{\bf Lower Hudson Regional Information Center} \hfill {\bf January 2016 to August 2016.}}\\
	BOCES, Systems and Operations Department \hfill http://www.lhric.org/\\
	Worked as part of a team offering backup, Disaster recovery, email, and web filtering solutions to our clients. I worked with commvault, and the Microsoft System Center Configuration Manager.
	\begin{itemize}[topsep=1ex, itemsep=.5ex, parsep=0ex, partopsep=.75ex]
		\item[]{\bf Intern Project: Imaging Solution}\\
		The goal of the project was to setup and deploy an instance of the Microsoft System Center Configuration Manager and utilize it to offer an desktop imaging service for our clients. 
	\end{itemize}
	\item[]{{\bf Lower Hudson Regional Information Center} \hfill {\bf June 2015 to August 2015.}}\\
	BOCES, Finance Department \hfill http://www.lhric.org/\\
	Worked with experienced members of the Finance department to maintain the New York
	State databases that reflected the updated tenure and seniority information of select schools in Westchester county.
\end{itemize}

\section*{Hobbies}
\begin{itemize}[topsep=1ex, itemsep=.5ex, parsep=0ex, partopsep=.75ex]
	\item[]{\bf Juggling}\\
	I garnered a passion for juggling and the juggling community from my time with the RIT Juggling Club. As a former president, I helped facilitate one of the longest running regional juggling conventions in the United States, The RIT Juggle-In.

	\item[]{\bf RIT Computer Science House}\\
	An Active Alumni of the RIT Computer Science House.
\end{itemize}
\end{document}
